% arara: pdflatex

\documentclass[a4paper,11pt]{article}
\usepackage[left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm]{geometry}
\usepackage{times} % Use Helvetica font
\renewcommand{\familydefault}{\sfdefault}
\usepackage{parskip} % Better paragraph spacing
\usepackage{hyperref}

\begin{document}

\begin{flushright}
\textbf{Jesper Hasselquist} \\
Vikingavagen 18A \\
224 77 Lund \\
Sweden \\
jesper.hasselquist@pm.me \\
+46708258116 \\
\today \\
\end{flushright}

\vspace{1cm}

\textbf{Subject: Application for Web Service Developer Engineer Position}  \\

Dear Hiring Manager,

I am excited to apply for the Web Service Developer Engineer position at Capcom. As an experienced engineering manager and developer with a strong background in JavaScript, Node.js, and frontend technologies, I am eager to contribute to Capcom's gaming ecosystem.

With over three years of leadership experience, I have honed my skills in collaboration, technical decision-making, and delivering high-quality web solutions. My expertise includes JavaScript, Node.js, and frontend development using React and TypeScript, though I prefer Svelte and JSDoc for efficient, maintainable interfaces. I have worked on projects such as developing a Salesforce integration, leading extensive security reviews, and driving the adoption of conventional commits for automated changelog generation. Additionally, I contributed to a frontend application that enables customers to embed a chat widget and phone queue information on their websites.

Passionate about gaming, I am eager to work on interactive web systems that enhance player experiences. I thrive in team environments, embracing new technologies and optimizing workflows to improve efficiency and user engagement. Capcom’s dedication to innovation strongly resonates with me, and I would be honored to contribute to these efforts.

I am also highly motivated to relocate to Japan, both for this opportunity and to be closer to my partner. I look forward to the possibility of joining your team and contributing to Capcom’s success.

Thank you for your time and consideration. I would welcome the opportunity to discuss how my skills align with your needs.

\vspace{1cm}

Best regards,  \\
\textbf{Jesper Hasselquist}

\end{document}
